---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pkgTS

<!-- badges: start -->
<!-- badges: end -->

The goal of R package `pkgTS` is to provide functions for time series analysis, 
e.g. ussable for climate or corona virus spread analysis.


## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("WoVollmer/pkgTS")
```
## Example

This is a basic example which shows you how to plot corona time series data:

```{r example}
library(pkgTS)
## basic example code
ggts_cum_daily(corona_data, country = "Germany", weeks = 6)

# note for display on GitHub:
#  resulted plot files in /man/figures to be committed and pushed to package
```


## Corona Virus Dashboard

The **`Corona Virus Dashboard`** provides analysis of the time series data provided by the **Johns Hopkins University** on GitHub. For links and references see the Dashboard-file *Corona Virus Dashboard Web Site* rsp. RMD-file *Corona_Virus_TS_Dashboard.Rmd*.

The 
[Corona_Virus_TS_Dashboard.Rmd](https://github.com/WoVollmer/R-TimesSeriesAnalysis/tree/master/Corona-Virus)
file is stored on GitHub repository.

The [Corona Virus Dashboard Web Site](https://wovollmer.github.io/github.io/) 
is published as **GitHub page**
