---
title: "Vignette pkgTS TimeSeries Functions"
output: rmarkdown::html_vignette
author: "WoVollmer"
date: '`r Sys.Date()`'
vignette: >
  %\VignetteIndexEntry{Vignette pkgTS TimeSeries Functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}

knitr::opts_chunk$set(fig.width = 7, fig.asp = 0.618)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(pkgTS)
```


# R Files

Up to now following R files are part of the package:

```{r, echo = TRUE}

dir("./../R/")

```


# Corona data and example figure

The data for the ggts_corona functions are a `data.frame` /  `tibble` 
with following structure:

## Data *long* format with `Case_Type = Confirmed | Deaths`:

```{r}

tail(corona_data %>% dplyr::filter(Country == "Germany"))


```

## Data *wide* format creation with dissolved `Case_Type`:

```{r}

tail(uts_get_corona_data_wide(
  corona_data %>% dplyr::filter(Country == "Germany")))

```


## Figure

Basic example plot of corona time series data:

```{r, fig.show='hold'}

ggts_cum_daily(corona_data, country = "Germany", weeks = 6)

```


## Corona Virus Dashboard

> The **`Corona Virus Dashboard`** provides analysis of the time series data provided by the **Johns Hopkins University** on GitHub. For links and references see the Dashboard-file *Corona Virus Dashboard Web Site* rsp. RMD-file *Corona_Virus_TS_Dashboard.Rmd*.

The 
[Corona_Virus_TS_Dashboard.Rmd](https://github.com/WoVollmer/R-TimesSeriesAnalysis/tree/master/Corona-Virus)
file is stored on GitHub repository.

The [Corona Virus Dashboard Web Site](https://wovollmer.github.io/github.io/) 
is published as **GitHub page**


# Climate data and example figure

The data for the ggts_climate functions are a `data.frame` /  `tibble` 
with following structure:

## Data *long* format with `Measure = Temperature | Precipitation`:

```{r}

head(monthly_climate_basel)

tail(monthly_climate_basel)

```

## Data *wide* format with `Measure = CO2`:

```{r}

tail(monthly_co2_wide)

```


## Figure

Basic example plot of climate time series data:

```{r, fig.show='hold'}

plot_monthly <- ggts_year_over_month(monthly_climate_basel %>%
                                       dplyr::filter(Measure == "Temperature"), period = Year)

plot_monthly
plot_monthly + ggplot2::coord_polar("x", start = pi)

ggts_year_over_month(monthly_climate_basel, period = Year) +
  ggplot2::facet_wrap(~Measure, ncol = 1, scales = "free_y")
```
